---
pdf_document: default
author: "Wong Wei Qi"
date: '`r Sys.Date()`'
output:
  html_document: null
  df_print: paged
  pdf_document: default
title: "Week-5: Code-along"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# II. Code to edit and execute using the Code-along.Rmd file 
<br>

## A. Writing a function
<br>

### 1. Write a function to print a "Hello" message (Slide #14)

```{r, eval=TRUE,echo=TRUE}
say_hello_to <- function(name) {
  print(paste0("Hello ", name, "!"))
}

```
<br>

### 2. Function call with different input names (Slide #15)

```{r, eval=TRUE,echo=TRUE}

print(say_hello_to('Wei Qi'))

```
<br>

### 3. typeof primitive functions (Slide #16)

```{r, eval=TRUE,echo=TRUE}

typeof(sum)

```
<br>

### 4. typeof user-defined functions (Slide #17)

```{r, eval=TRUE,echo=TRUE}
typeof(say_hello_to)
```

### 5. Function to calculate mean of a sample (Slide #19)

```{r, eval=TRUE,echo=TRUE}

calc_sample_mean <- function(sample_size) {
  mean(rnorm(sample_size))
}

```
<br>

### 6. Test your function (Slide #22)

```{r, eval=TRUE,echo=TRUE}
calc_sample_mean(100)

```

### 7. Customizing the function to suit input (Slide #23)

```{r, eval=TRUE,echo=TRUE}

library(tidyverse)

# creating a vector to test our function
sample_tibble <- tibble(
  sample_sizes =
    c(100, 300, 3000)
)
# using rowwise groups the data by row, # allowing calc_sample_mean
sample_tibble %>%
  group_by(sample_sizes) %>%
  mutate(
    sample_means =
      calc_sample_mean(sample_sizes)
  )
```
<br>

### 8. Setting defaults (Slide #25)

```{r, eval=TRUE,echo=TRUE}
# First define the function
calc_sample_mean <- function(sample_size, our_mean=0, our_sd=1) {
  sample <- rnorm(sample_size,
                  mean = our_mean,
                  sd = our_sd)
   mean(sample)
}

calc_sample_mean(100)
# Call the function 
```
<br>

### 9. Different input combinations (Slide #26)

```{r, eval=TRUE,echo=TRUE}
calc_sample_mean(10, our_sd = 2)
```
<br>

### 10. Different input combinations (Slide #27)

```{r, eval=TRUE,echo=TRUE,error=TRUE} 
# set error=TRUE to see the error message in the output
calc_sample_mean(our_mean = 5)
```
<br>

### 11. Some more examples (Slide #28)

```{r, eval=TRUE,echo=TRUE,error=FALSE} 
add_two <- function(x) { x+2
}
## B. Scoping

add_two(-34)

### 12. Multiple assignment of z (Slide #36)

```{r, eval=FALSE,echo=TRUE}
foo <- function(z = 2) { # reassigning z
z <- 3
return(z+3)
}
foo()

```
<br>

### 13. Multiple assignment of z (Slide #37)

```{r, eval=TRUE,echo=TRUE}
z <-1 
foo <- function(z=2) {
  z<-3
  return(z+3)
}

foo(4)
```
<br>