---
title: "Challenge-4"
author: "Wong Wei Qi"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
p.comment {
background-color: #DBDBDB;
padding: 10px;
border: 1px solid black;
margin-left: 25px;
border-radius: 5px;
font-style: italic;
}

</style>

## Questions
<br>

Load the "CommQuest2023.csv" dataset using the `read_csv()` command and assign it to a variable named "comm_data." 

```{r, eval=TRUE,echo=TRUE}
library(tidyverse)
comm_data <- read_csv('CommQuest2023_Larger.csv')

```
<br>


#### Question-1: Communication Chronicles

Using the select command, create a new dataframe containing only the "date," "channel," and "message" columns from the "comm_data" dataset.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
new<-
comm_data %>%
  select(date,channel,message)
new
```
<br>

#### Question-2: Channel Selection

Use the filter command to create a new dataframe that includes messages sent through the "Twitter" channel on August 2nd.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
new %>% 
  filter(
    channel == 'Twitter' , date == '2023-08-02'
  ) 
```
<br>

#### Question-3: Chronological Order

Utilizing the arrange command, arrange the "comm_data" dataframe in ascending order based on the "date" column.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
comm_data %>%
  arrange(date)
```
<br>

#### Question-4: Distinct Discovery

Apply the distinct command to find the unique senders in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
comm_data %>%
  distinct(sender)
```
<br>

#### Question-5: Sender Stats

Employ the count and group_by commands to generate a summary table that shows the count of messages sent by each sender in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
comm_data %>%
  group_by(sender) %>%
  summarise(count = n())
```
<br>

#### Question-6: Channel Chatter Insights

Using the group_by and count commands, create a summary table that displays the count of messages sent through each communication channel in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
comm_data %>%
  group_by(channel) %>%
  summarise(count = n())

```
<br>

#### Question-7: Positive Pioneers

Utilize the filter, select, and arrange commands to identify the top three senders with the highest average positive sentiment scores. Display their usernames and corresponding sentiment averages.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
  comm_data %>%
  arrange(desc(sentiment)) %>%
  filter(sender >= 0) %>%
  select(sender, sentiment) %>%
  slice(1:3)
  
  
```
<br>

#### Question-8: Message Mood Over Time

With the group_by, summarise, and arrange commands, calculate the average sentiment score for each day in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
  comm_data %>%
  group_by(date) %>%
  summarise(mean_sentiment = mean(sentiment)) %>%
  arrange(date)

```
<br>

#### Question-9: Selective Sentiments

Use the filter and select commands to extract messages with a negative sentiment score (less than 0) and create a new dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
  new_dtf <-
   comm_data %>%
   filter(
     sentiment < 0
   ) %>%
   select(message,sentiment)
 new_dtf
```
<br>

#### Question-10: Enhancing Engagement

Apply the mutate command to add a new column to the "comm_data" dataframe, representing a sentiment label: "Positive," "Neutral," or "Negative," based on the sentiment score.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
comm_data %>%
  mutate(sentiment_label = case_when(
    sentiment > 0 ~ "Positive",
    sentiment < 0 ~ "Negative",
    TRUE ~ "Neutral" # Everything else is Neutral
  ))
```
<br>

#### Question-11: Message Impact

Create a new dataframe using the mutate and arrange commands that calculates the product of the sentiment score and the length of each message. Arrange the results in descending order.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
new<-
comm_data%>%
  mutate(product_sentiment_length=sentiment*nchar(message))%>%
  arrange(desc(product_sentiment_length))
new
```
<br>

#### Question-12: Daily Message Challenge

Use the group_by, summarise, and arrange commands to find the day with the highest total number of characters sent across all messages in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
comm_data %>%
  group_by(date) %>%
  summarise(num_char = sum(nchar(message))) %>%
  arrange(desc(num_char)) %>%
  slice(1)

```
<br>

#### Question-13: Untidy data

Can you list at least two reasons why the dataset illustrated in slide 10 is non-tidy? How can it be made Tidy?

**Solution:** 
1.Each observation has different units of measurement across each attribute, hence they cannot be measured and compared equally among the observation.

2. There is a mix of data types in each cell of the dataset, hence it will be difficult to manipulate the variables.

It can be tidy by removing units, and maintain that each variable has the same units of measurement.